A Domain Specific Language for SpectreGuard

### 2020-12-07 paper/main.tex
Center generated code figure
Barendregt convention

This also outlines procedure that the C code generator uses. When code written
in the EDSL is transformed into C code, a name generator first annotates the abstract syntax tree
(AST). This annotated AST can be used by both the code generator and the information flow
leak analysis tool (the latter is described in Section \ref{sec:Analysis}).

@@

\begin{figure}
\begin{lstlisting}{language=C}
int _fs_0[8] __attribute__((nospec))__;
int _fs_1[8];
for (int _fs_2 = 0; _fs_2 < 8; _fs_2 = _fs_2 + 1) {
  int _fs_3 = 0;
  for (int _fs_4 __attribute__((nospec))__ = 0 ;
      fs_4 < (_fs_0[_fs_2]);
      _fs_4 = _fs_4 + 1) {
    _fs_3 = _fs_3 + 1;
  }
  _fs_1[_fs_2] = _fs_3;
}
\end{lstlisting}
\caption{C code generated from \ttt{example4}}
\label{fig:GenC4}
\end{figure}

>>>>

This also outlines procedure that the C code generator uses. When code written
in the EDSL is transformed into C code, a name generator first annotates the
abstract syntax tree (AST) with globally unique names (enforcing the Barendregt
variable convention; see Chapter 2 in~\cite{BarendregtConversion}). This annotated AST can be used by both the code generator and the
information flow leak analysis tool (the latter is described in Section
\ref{sec:Analysis}).

@@

\begin{figure}
\begin{center}
\begin{tabular}{c}
\begin{lstlisting}{language=C}
int _fs_0[8] __attribute__((nospec))__;
int _fs_1[8];
for (int _fs_2 = 0; _fs_2 < 8; _fs_2 = _fs_2 + 1) {
  int _fs_3 = 0;
  for (int _fs_4 __attribute__((nospec))__ = 0 ;
      fs_4 < (_fs_0[_fs_2]);
      _fs_4 = _fs_4 + 1) {
    _fs_3 = _fs_3 + 1;
  }
  _fs_1[_fs_2] = _fs_3;
}
\end{lstlisting}
\end{tabular}
\end{center}
\caption{C code generated from \ttt{example4}}
\label{fig:GenC4}
\end{figure}
